Analysis

### 2021-12-15 code/R/Analysis.Rmd
Added plotting of evaluation results

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(stringr)
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(stringr)
library(GGally)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
d = read.csv("U:/BITCue/Projekter/TrackingFlowers/code/7temptest_eval.csv")

d %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")
```

```{r}
d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/code/8temptest_eval_THUL01.csv")

d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

```{r}
remotes::install_github("tylermorganwall/rayshader")
library(rayshader)
library(tidyverse)
measles = read_csv("https://tylermw.com/data/measles_country_2011_2019.csv")
melt_measles = reshape2::melt(measles, id.vars = c("Year", "Country", "Region", "ISO3"))
melt_measles$Month = melt_measles$variable
melt_measles$cases = melt_measles$value
melt_measles %>% 
  group_by(Year, Month) %>%
  summarize(totalcases = sum(cases,na.rm = TRUE)) %>% 
  mutate(totalcases = ifelse(Year == 2019 & !(Month %in% c("January","February","March")), NA, totalcases)) %>%
  ggplot() + 
  geom_tile(aes(x=Year, y=Month, fill=totalcases,color=totalcases),size=1,color="black") + 
  scale_x_continuous("Year", expand=c(0,0), breaks = seq(2011,2019,1)) +
  scale_y_discrete("Month", expand=c(0,0)) +
  scale_fill_viridis("Total\nCases") +
  ggtitle("Reported Worldwide Measles Cases") +
  labs(caption = "Data Source: WHO") +
  theme(axis.text = element_text(size = 12),
        title = element_text(size = 12,face="bold"),
        panel.border= element_rect(size=2,color="black",fill=NA)) -> 
measles_gg

plot_gg(measles_gg, multicore = TRUE, width = 6, height = 5.5, scale = 300, 
background = "#afceff",shadowcolor = "#3a4f70")
```
